---
title: "Working with a Colletion of Objects"
author: "Łukasz A. Bartnik"
date: "February 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Create a collection

It's really a handle, the collection exists in the storage even when the
handle is no longer accessible.

Create a collection handle:
  * name of this collection in `some collection`
  * it is stored in the local filesystem
  * it is stored in the current working directory
  

```{r}
handle <- collection('some collection', create = TRUE, storage = filesystem(getwd()))

handle <- collection('some collection', create = TRUE)
```



# Store objects in a collection


`store(object, handle, name)`

  * store `object`
  * in collection pointed to by `handle`
  * and group them under name `name`

methods for `object` of class:
  * `list` - store each element separately, group them under `name`
  * `clist` - as above
  * any other - treat as a single object



```{r}

energy <- collection('energy')

list(ts1, ts2, ts3) %>% store(energy, 'data')

list(lm(...), lm(...), lm(...)) %>% store(energy, 'models')

```



# Apply a function on (all) objects

`capply(clist, function)`

`capply(handle, function)`


```{r}
energy <- collection('energy')

energy %>% capply(function(...){})

energy %>% filter(tag = value) %>% capply(function(...){}, .lazy = FALSE)

# single process
res <- energy %>% filter(tag = value) %>% capply(function(...){}) %>% local

# multiple processes
res <- energy %>% filter(tag = value) %>% capply(function(...){}) %>% local(cores = 4)

# pass results back to the collection, potentially might speed-up the computation
energy %>% filter(tag = value) %>% capply(function(...){}) %>% store(energy, 'attempt #3')
```



# Extra settings

```{r}
options(colletions.cores = 4)

# return immediately; might not work if result is to be returned
# into a variable, in the session from which it is called
options(colletions.async = TRUE)
```


